Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-07-04 paper/ms.tex
Incorporate JNW suggestions (part 2)
Co-authored-by: joshwinn <jwinn@astro.princeton.edu>
Remove needless howevers
Co-authored-by: joshwinn <jwinn@astro.princeton.edu>

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC 2602.  The
  star and validated planet are therefore between 30 and 46 million
  years old.  The planet is warm ($P = 8.32\,{\rm d}$) and roughly
  Jupiter-sized.  However, its transits are grazing: $b > 0.92$ at
  3$\sigma$.  From TESS photometry alone, the planetary size lies
  within 0.68--8.24 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
  percentile), due to the degeneracy between the planetary size and
  the impact parameter of the transit.  From radial velocity
  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
  Jup}$ (3$\sigma$).  Grazing transits are cause for concern: they
  usually are indicative of astrophysical false positive scenarios.
  Our follow-up data show that such scenarios are highly unlikely.
  Our combined multi-color photometry, high-resolution imaging, and
  radial velocities rule out hierarchical eclipsing binary scenarios.
  Background eclipsing binary scenarios, though limited by speckle
  imaging, formally remain a 0.2\% possibility.  TOI 837.01 is
  therefore a validated adolescent exoplanet.  Further observations of
  its stellar obliquity, atmosphere, and mass should confirm its
  planetary nature beyond doubt, and could improve our understanding
  of how the physical and orbital properties of exoplanets change in
  time.
\end{abstract}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.9\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf TESS light curve of \tn\ from Sectors 10 and 11.} {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Spot-induced stellar variability is the dominant signal; flares
    are shown with gray crosses.  Dashed lines indicate the five
    transits observed by TESS.  {\it Bottom}: Zoomed windows of
    individual transits.  Gray lines are the best-fit transit model,
    which includes a local quadratic trend in each window.
		\label{fig:rawzoom}
	}
\end{figure*}

@@

If the transit were box-shaped, this argument could be extended to
even more restrictive depths \citep[{\it
e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}
However, since the transits of \tn\ are grazing, the second and third
contact points do not occur, and the shape of the transit is not
restrictive.

@@

% results from 20200624_simple_fpp_weak_sec 
We ran \texttt{VESPA}\footnote{We used \texttt{VESPA-0.6} and
\texttt{isochrones-1.2.2}.}, and directly incorporated our constraints
of the SOAR $I$-band contrast curve and a non-detection of secondary
eclipses with a depth set at roughly twice the limits from the SPOC
vetting report (0.1\%).  We verified that changing the secondary
eclipse depth limit did not significantly affect the results.  We set
the maximum aperture radius at $2''$, based on our ground-based
photometry.  Incorporating the constraints from
Figure~\ref{fig:fpscenario}, our nominal false positive probability
analysis excluded EB and HEB scenarios.  This yielded an FPP of 0.21\%
for \pn, sufficient for formal validation as a planet
\citep{morton_efficient_2012}.  We did not incorporate our constraint
that \tn\ is not double-lined, which rules out an additional portion
of BEB parameter space.  Had we not acquired multicolor ground-based
photometry, and been unable to exclude HEB scenarios, the FPP would
have risen to 8\%.  However, since the transits are achromatic
(Figure~\ref{fig:jointphot}), particularly in Johnson-B band, we can
rule out HEB scenarios.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f10.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{ 
		{\bf Posterior probabilities of
			impact parameter, planet-to-star size ratio, and stellar density.} The photometric
		data fitted in Section~\ref{subsec:planet} allow for
		nonphysical planet sizes ($R_{\rm p}>2R_{\rm Jup}$;
		$\log(R_{\rm p}/R_\star) \gtrsim -1.6$) due to a classic degeneracy
		between the planet size and impact parameter.  Non-planetary sizes
		would however imply non-planetary masses, which are ruled out by our
		radial velocity measurements.
		This plot was made using \texttt{corner} \citep{corner_2016}.
		\label{fig:subsetcorner}
	}
\end{figure}

>>>>

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC 2602.  The
  star and validated planet are therefore between 30 and 46 million
  years old.  The planet is warm ($P = 8.32\,{\rm d}$) and roughly
  Jupiter-sized.  Its transits are grazing: $b > 0.92$ at
  3$\sigma$.  From TESS photometry alone, the planetary size lies
  within 0.68--8.24 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
  percentile), due to the degeneracy between the planetary size and
  the impact parameter of the transit.  From radial velocity
  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
  Jup}$ (3$\sigma$).  Grazing transits are cause for concern: they
  usually are indicative of astrophysical false positive scenarios.
  Our follow-up data show that such scenarios are highly unlikely.
  Our combined multi-color photometry, high-resolution imaging, and
  radial velocities rule out hierarchical eclipsing binary scenarios.
  Background eclipsing binary scenarios, though limited by speckle
  imaging, formally remain a 0.2\% possibility.  TOI 837.01 is
  therefore a validated adolescent exoplanet.  Further observations of
  its stellar obliquity, atmosphere, and mass should confirm its
  planetary nature beyond doubt, and could improve our understanding
  of how the physical and orbital properties of exoplanets change in
  time.
\end{abstract}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.85\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf TESS light curve of \tn\ from Sectors 10 and 11.} {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Spot-induced stellar variability is the dominant signal; flares
    are shown with gray crosses.  Dashed lines indicate the five
    transits observed by TESS.  {\it Bottom}: Zoomed windows of
    individual transits.  Gray lines are the best-fit transit model,
    which includes a local quadratic trend in each window.
		\label{fig:rawzoom}
	}
\end{figure*}

@@

If the transit were box-shaped, this argument could be extended to
even more restrictive depths \citep[{\it
e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}
Since the transits of \tn\ are grazing, the second and third
contact points do not occur, and the shape of the transit is not
restrictive.

@@

% results from 20200624_simple_fpp_weak_sec 
We ran \texttt{VESPA}\footnote{We used \texttt{VESPA-0.6} and
\texttt{isochrones-1.2.2}.}, and directly incorporated our constraints
of the SOAR $I$-band contrast curve and a non-detection of secondary
eclipses with a depth set at roughly twice the limits from the SPOC
vetting report (0.1\%).  We verified that changing the secondary
eclipse depth limit did not significantly affect the results.  We set
the maximum aperture radius at $2''$, based on our ground-based
photometry.  Incorporating the constraints from
Figure~\ref{fig:fpscenario}, our nominal false positive probability
analysis excluded EB and HEB scenarios.  This yielded an FPP of 0.21\%
for \pn, sufficient for formal validation as a planet
\citep{morton_efficient_2012}.  We did not incorporate our constraint
that \tn\ is not double-lined, which rules out an additional portion
of BEB parameter space.  Had we not acquired multicolor ground-based
photometry, and been unable to exclude HEB scenarios, the FPP would
have risen to 8\%.  Since the transits are achromatic
(Figure~\ref{fig:jointphot}), particularly in Johnson-B band, we can
rule out HEB scenarios.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f10.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{ 
    {\bf Posterior probabilities of impact parameter, planet-to-star
    size ratio, and stellar density.} The photometric data fitted in
    Section~\ref{subsec:planet} allow for nonphysical planet sizes
    ($R_{\rm p}>2R_{\rm Jup}$; $\log(R_{\rm p}/R_\star) \gtrsim -1.6$)
    due to a classic degeneracy between the planet size and impact
    parameter.  Non-planetary sizes would imply non-planetary masses,
    which are ruled out by our radial velocity measurements.  This
    plot was made using \texttt{corner} \citep{corner_2016}.
		\label{fig:subsetcorner}
	}
\end{figure}
